---
title: "GraphsT1"
author: "Marlise Hofer"
date: "November 19, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```
# Let's look at some scatterplots!
```{r}
#First, load some packages!

library(tidyverse)
library(knitr)
library(ggthemes)
library(ggplot2)

#Set working directory & load data
setwd("~/Dropbox/research/Role of Smell in Stress Reduction/dominance communication between men/TStudiesR")

data <- read.csv("t_study1.csv", header=TRUE)
```

#Plot T against pleasantness & compute correlation
ave_ple=plesantness

```{r}
data %>% 
	ggplot(aes(x = test, y = avg_ple)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

cor.test(data$avg_ple, data$test)
```

correlation - r=0.035  p=.036

#Exact same results with Zscored variables

```{r}
data %>% 
	ggplot(aes(x = Ztest, y = Zavg_ple)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

```

#Pleasantness has one variable with Zscore of over 3
What happens when we filter out that variable?

```{r}
data %>% 
	filter (shirt_code != "31") %>% 
	ggplot(aes(x = Ztest, y = Zavg_ple)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

data1 <- filter (data, shirt_code != "31")
cor.test(data1$Zavg_ple, data1$Ztest)
```
correlation is stronger - r=0.039 p=.021

#Now let's check the correlation while also removing the clean shirt
```{r}

data2 <- filter (data, shirt_code != "31", shirt_code != "37")
cor.test(data2$Zavg_ple, data2$Ztest)

```
correlation - r=0.035 p = .044. Correlation is still there and significant.

#Okay, now I'll look at graphs of dominance and prestige with T
```{r}
data %>% 
	ggplot(aes(x = Ztest, y = Zavg_dom)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)
cor.test(data$Zavg_dom, data$Ztest)

data %>% 
	ggplot(aes(x = Ztest, y = Zavg_pre)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)
cor.test(data$Zavg_pre, data$Ztest)
```

#Now I'll look at a graph of dominance with pleasantness
```{r}
data %>% 
	ggplot(aes(x = Zavg_dom, y = Zavg_ple)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

cor.test(data$Zavg_ple, data$Zavg_dom)
```
correlation r=0.56  p=.0004

#Take out the outlier in dominance (over 3 Zscore)
```{r}
data %>% 
	filter (shirt_code != "7")  %>% 
	ggplot(aes(x = Zavg_dom, y = Zavg_ple)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

data3 <- filter (data, shirt_code != "7")
cor.test(data3$Zavg_ple, data3$Zavg_dom)
```
correlation r=0.45  p=.006. No real change.

# Graphs of prestige with pleasantness
```{r}
data %>% 
	ggplot(aes(x = Zavg_ple, y = Zavg_pre)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

cor.test(data$Zavg_ple, data$Zavg_pre)
```
correlation r=0.93

#There seems to be no indication of any trend other than linear trends