---
title: "GraphsT1"
author: "Marlise Hofer"
date: "November 19, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```
#Exploring the T Study 1 data for only men

```{r}
#First, load some packages!

library(tidyverse)
library(knitr)
library(ggthemes)
library(ggplot2)

#Set working directory & load data
setwd("~/Dropbox/research/Role of Smell in Stress Reduction/dominance communication between men/TStudiesR")

data <- read.csv("t_study1_male.csv", header=TRUE)
```

#Plot T against pleasantness & compute correlation

```{r}
data %>% 
	ggplot(aes(x = Ztest, y = Zpleas)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

cor.test(data$Zpleas, data$Ztest)
```

#Pleasantness has one variable with Zscore of over 3
What happens when we filter out that variable?

```{r}
data %>% 
	filter (shirt_code != "31") %>% 
	ggplot(aes(x = Ztest, y = Zpleas)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

data1 <- filter (data, shirt_code != "31")
cor.test(data1$Zpleas, data1$Ztest)
```

#Now let's check while also removing the clean shirt
```{r}
data %>% 
	filter (shirt_code != "31", shirt_code != "37") %>% 
	ggplot(aes(x = Ztest, y = Zpleas)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

data2 <- filter (data, shirt_code != "31", shirt_code != "37")
cor.test(data2$Zpleas, data2$Ztest)

```

#Okay, now I'll look at graphs of dominance and prestige with T
```{r}
data %>% 
	ggplot(aes(x = Ztest, y = Zdom)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

data %>% 
	ggplot(aes(x = Ztest, y = Zpres)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)
```

#Now I'll look at a graph of dominance with pleasantness
```{r}
data %>% 
	ggplot(aes(x = Zdom, y = Zpleas)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

cor.test(data$Zpleas, data$Zdom)
```
#Pleasantness has one variable with Zscore of over 3
What happens when we filter out that variable?

```{r}
data %>% 
	filter (shirt_code != "31") %>% 
	ggplot(aes(x = Zdom, y = Zpleas)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

data4 <- filter (data, shirt_code != "31")
cor.test(data4$Zpleas, data4$Ztest)
```


# Graphs of prestige with pleasantness
```{r}
data %>% 
	ggplot(aes(x = Zpleas, y = Zpres)) + 
	geom_point() +
	geom_smooth(color = "purple", lwd = 1, se=TRUE)

cor.test(data$Zpleas, data$Zpres)
```

#There seems to be no indication of any quadratic effects